\section*{Conclusion}
\addcontentsline{toc}{section}{Conclusion}

In summary, whilst proving the JCF, many interesting characteristics of linear maps emerge and are put to use. This is seen in how the eigenspaces divide the vector space into manageable subspaces and how the map remains invariant over these spaces.

During the process we realized that the vector space can be partitioned into subspaces that are built from the eigenspaces. Iterating maps were the key to expanding the eigenspaces, and proved to be a more useful concept than initially thought. The idea of iterating the maps lead us to the definition of the null chains. Because of their many properties, they play a major role as a basis of the vectorspace. 

After concluding the JCF proof, we turned our attention to the more general problem of proving the WCF.
We needed new definitions for eigenvalues and eigenvectors that comply to our new algebraic structure: matrix pencils. In defining the generalized eigenvalues, we found that some of them do not appear in the polynomial characterized by the determinant of the matrix pencil.
We call them infinite eigenvalues, as they are the zero eigenvalue of the reverse matrix pair.
In order to account for both types of eigenvalues, we looked for two bases for the vectorspace, each divided into two parts.
We pick the bases as a collection of chains again, with a definition that incorporates the behaviour of both linear transformations.
Using the two bases we can create their corresponding transformation matrices which when applied to the matrix pair puts it into WCF. Geometrically these transformations are independent changes of basis for the domain and codomain of the matrices that define the pencil.

Clearly some ideas pervade both these proofs. The theme of vector-chains and decomposition into invariant subspaces reoccur in central roles. In fact the WCF can be proven without the use of the JCF, in which case the JCF follows immediately as a corollary for the case where the second matrix in the pair is the identity.

The importance and interconnection of both the WCF and JCF should now be evident. 




