\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{amsmath, amssymb, amsthm}
\usepackage{mathtools}
\usepackage{lettrine}

\usepackage[hidelinks]{hyperref}
\theoremstyle{definition}
\newtheorem{theorem}{Theorem}[subsection]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition} 
\newtheorem{corollary}[theorem]{Corollary} 
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{property}[theorem]{Property}
\newtheorem{remark}[theorem]{Remark}
\usepackage{xcolor}
\usepackage{amsthm}





\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Ker}{\operatorname{Ker}}
\newcommand{\im}{\operatorname{im}}
% \newcommand{\id}{\mathrm{id}}
\newcommand{\id}{I}
\newcommand{\Gi}{G_{\lambda_i}}

 


\title{Generalized eigenvalues and Weierstrass Form}
\author{Gloria, Bodhi, Branko, Albert}
\date{April 2026}

\begin{document}

\maketitle


\tableofcontents
\newpage
\section{Invariant subspaces}
\lettrine{W}{e}
consider a linear map $T:V\rightarrow V$, where $V$ is a finite dimensional vector space. For a random subspace $S\subset V$, its image under $T$ is usually also random.
Therefore we want to consider subspaces which preserve their structure under $T$, called invariant subspaces. 
\begin{definition}
    A subspace $S$ is called \textit{invariant} under the linear map $T$ if $$v\in S\implies T(v)\in S$$
\end{definition}
 
$\newline$Before we illustrate their effectiveness, we give some examples:\\
\subsection{Examples and properties}

    \begin{example}
    The well-known subspace $$E_\lambda = \{v: T(v)=\lambda v\}$$ is invariant - each element is scaled under $T$, which is still in $E_\lambda$.\\ \\
\end{example} 




\begin{example}\label{ex:invariance0}
    The image $$\im T=\{T(v): v\in V\}$$is invariant almost by definition: $$v\in T(V)\implies T(v)\in T(V) $$.
\end{example} 

\begin{example}\label{ex:invariance1}
    The generalized kernel $$K=\{v: \exists k\in \mathbb{N}^* \text{ s.t } T^k(v)=0\}$$
is invariant under $T$. This is indeed a subspace, and the invariance here follows from 
$$v\in K \implies \exists k\ s.t\ T^k(v)=0\implies T^{k-1}(T(v))=0\implies T(v)\in K\ (\text{definition}).$$
This set has a stronger structure than being just invariant. It can be seen that 
\begin{equation}\label{initial}
    v\notin K\implies T(v)\notin K
\end{equation}
which is not in general true for invariant subspaces.
\end{example}
\newpage
Because of their behavior, we want to search for building blocks of $V$ of invariant subspaces - similarly to how the integers are building blocks of primes. By building blocks, we mean invariant subspaces $$S_1,S_2,...,S_k$$such that for a basis $\beta_i$ for $S_i$, $$\bigcup_{i=1}^k \beta_i$$is a basis for $V$. Equivalently, $$\bigoplus_{i=1}^kS_k=V$$If we one succeeds in this, then there would be a matrix representation of $T$ in the form \[
\begin{pmatrix}
A_1 & 0   & \cdots & 0 \\
0   & A_2 & \cdots & 0 \\
\vdots & \vdots & \ddots & \vdots \\
0   & 0   & \cdots & A_k
\end{pmatrix}
\]
This structure is strictly due to the invariance of the subspaces - if $\beta_i$ is a basis for $S_i$ consisting of $\beta_{i1},\beta_{i2},...,\beta_{ik}$, then $$T(\beta_{ij})\in S_i\ \forall j\leq k, $$and therefore may be expressed only in terms of $\beta_{i1},\beta_{i2},...,\beta_{ik}$ - hence the above pattern.\\

Our goal is to achieve this decomposition with choosing the best possible invariant subspaces - so that the above $A_i$ blocks are of the simplest scheme.\\
It should already be obvious which invariant subspaces to start from. Before continuing, some properties:


\begin{property}
Invariant subspaces (except $\{\mathbf{0}\}$) $S$ under $T$ all contain an eigenvector of $T$. This is for the reason that the linear map

 $$T^*:S\rightarrow S\ \text{,} \ T^*(v)=T(v)$$   
is well defined due to the invariance. Then we just pick the eigenvector of $T^*$ (always exists).
    
\end{property}

\begin{lemma}\label{lem:invariance2}
    $$S\ \text{invariant under } T\iff S\ \text{invariant under } T-x\id\ \forall x\in \C,$$ and consequently invariant under any polynomial $P(T)$.
\end{lemma}



\section{The Jordan form}
In search of a canonical matrix representation of any $T$ -  
we begin with considering the eigenspaces. Let the eigenvalues be $\lambda_1, \lambda_2,...,\lambda_m$ for a linear operator $T$ over $V$, and the corresponding eigenspaces $$E_{\lambda_{i}}=\{v: T(v)=\lambda_i v\}$$
It is important to know that $$E_{\lambda_i}\cap E_{\lambda_j}=\{0\}  \ \text {, for all }i<j\leq k,$$and that for an arbitrary basis $\beta_i$ for $E_{\lambda_i}$, the set $$\bigcup_{i=1}^{m} \beta_i$$is linearly independent.$\newline$$\newline$
Is $\bigoplus_{i=1}^{m} E_{\lambda_i} = V$ true? - if yes, $\bigcup \beta_i$ may be our basis. 
Sadly, this is often not the case. An example is the matrix \[
A = \begin{pmatrix}
1 & 1 & 0 \\
0 & 1 & 1 \\
0 & 0 & 1
\end{pmatrix}
\]
with its corresponding linear map. If $\bigoplus E_{\lambda_i}$ is not enough to cover $V$, we want to somehow expand each $E_{\lambda_i}$ into a bigger subspace, with the importance to keep their invariance and disjointedness. $\newline \newline$

\subsection{Method}For each $E_{\lambda_i}$, consider $$G_{\lambda_i}=\bigcup_{i=1}^{\infty} \ker(T-\lambda_i \id)^k$$Denote $X^k_i=\ker(T-\lambda_i \id)^k$ and notice that $E_{\lambda_i}=X^1_i$. It can be seen that $$X^k_i\subseteq X^{k+1}_{i}$$ which means that for each iteration of $k$, the subspace $X^k_i$ grows. Each $X^k_i$ has 2 nice properties: it is nilpotent under $T-\lambda_i\id$ (definition), and invariant under $T-x\id\ \forall x\in \C $ which actually follows from the former. \\

\begin{lemma}
    For each $k\in \mathbb{N}, $$X^k_i$ is invariant under $T-x\id\ \forall x\in \C$
 \end{lemma}

\begin{proof}
    Follows from \ref{ex:invariance1} together with \ref{lem:invariance2}
\end{proof}

Notice that because $X^k_i\subseteq X^{k+1}_{i}\subseteq V \ \forall k$, after some iteration $N$ we must have $$X^k_i=X^{k+1}_{i}\  \forall k\geq N$$since we are bounded by the dimension of $V$.
$\\$ $\\$ Our final extendable subset is $G_{\lambda_i}=X^N_i$.

\begin{corollary}\label{col: invariance3}
    $G_{\lambda_i}$ is invariant under $T-x\id\ \forall x\in \C.$
\end{corollary}

$\newline$There is an obvious way to pick an appropriate basis for $G_{\lambda_i}$. Recall that each $v\in G_{\lambda_i}$ eventually gets mapped to $0$ under $T-\lambda_i\id$ (in other words, $T-\lambda_i I$ is nilpotent on $G_{\lambda_i}$), so it is natural to look at the vectors from the sequence $$v,(T-\lambda_i\id)(v), (T-\lambda_i\id)^2(v),...$$
\begin{definition}
    A \textit{null-chain} under a map $T$ is a set of (one or more) \textbf{non-zero} vectors $$\{v_1,v_2,..v_n\}$$such that $$T(v_i)=v_{i+1}\text{ for }i\leq n-1 $$and $$T(v_n)=0$$
\end{definition}
As one may guess:
\begin{lemma}\label{lemma:nullchain indp}
    A null-chain under any $T$ forms a linearly independent set.
\end{lemma}  

\begin{proof}
    Consider a null-chain $$\{v_1,v_2,...,v_n\}$$ and let 
    \begin{equation}\label{null}
        c_1v_1+c_2v_2+...+c_nv_n=0.
    \end{equation}

    
$\newline$Applying $T^{n-1}$ on both sides gives $$c_1T^{n-1}(v_1)+...+c_nT^{n-1}(v_n)=0\implies c_1v_n=0\implies c_1=0.$$
Substituting back in (\ref{null}) and applying $T^{n-2}$ on both sides gives $$c_2v_n=0\implies c_2=0.$$
Thus, inductively we obtain $$c_1=c_2=...=c_n=0$$
\end{proof} 

\begin{corollary}\label{col: nullchainS}
    A collection of null-chains forms a linearly independent set.\\ \\
    The argument for this is similar to Lemma \ref{lemma:nullchain indp}
    
\end{corollary}

    

$\newline$So we can pick null-chain in $G_{\lambda_i}$ under $T-\lambda_i\id$, and it is of question whether it can be a basis for $G_{\lambda_i}$. It usually is not, unfortunately. For example the matrix \[
A=\begin{pmatrix}
2&1&0\\
0&2&0\\
0&0&2
\end{pmatrix}
\]has $G_2$ with dimension $3$ for the eigenvalue $2$, but the longest null-chain is of size $2$ so one is not enough.\\ \\
The idea is to pick multiple such chains. In general: 
\begin{theorem}\label{theorem:multnull}
    A non-zero dimensional vector space $V$ under a nil-potent map $L$ always has a basis composed of null-chains. 
\end{theorem} 
\begin{proof}
    We show this via strong induction on the dimension of $V$.
    Consider a vector space $V$ under under a nilpotent map $L$ with $$dimV=1.$$Any $v\in V$ is a basis of $V$, and since $L(v)=0$, the null-chain $$\{v\}$$is a basis.\\
    Now that we have our base case, let $$dimV=k,$$hypothesizing that $$\text{\textit{every vector space with dimension} $\leq k-1$ \textit{which is nilpotent under $L$ has a basis of null-chains.}}$$\\
    The map $L$ is obviously non-invertible on $V$, therefore
    \begin{equation}\label{2}
        dim\ L(V)<dim(V)
    \end{equation}
    where $L(V)$ is the image under $L$. \\
    Dimension theorem for $L$ on $V$ says 
    \begin{equation}
        dim \ V=dim(L(V))+ dim(ker(L))
    \end{equation}
    Note that $L(V)$ is a subspace of $V$, therefore it is nilpotent under $L$. Considering (\ref{2}), by the induction hypothesis there is a basis of $L(V)$ of the form \[
\begin{aligned}
C_1 &= \{\beta_{11}, \beta_{12}, \ldots, \beta_{1k_1}\},\\
C_2 &= \{\beta_{21}, \beta_{22}, \ldots, \beta_{2k_2}\},\\
&\vdots\\
C_l &= \{\beta_{l1}, \beta_{l2}, \ldots, \beta_{lk_l}\}.
\end{aligned}
\]
where $C_i$'s are mutually disjoint nullchains s.t 
\[
\begin{aligned}
L(\beta_{i1}) &= 0\\
L(\beta_{i(k+1)}) &= L(\beta_{ik}).
\end{aligned}
\]
The first vector in each chain is in $ker(L)$ and therefore
\begin{equation}
    l\leq dim \ ker(L)
\end{equation}
because of the linear independence of the $\beta_{i1}$'s.\\
Consider the last vector $\beta_{ik_i}$ in each chain - it is in $L(V)$, therefore
\begin{equation}
    \forall i\leq l, \exists u_i\ s.t \ L(u_i)=\beta_{ik_i}
\end{equation}
Therefore we have obtained the new chains
\begin{equation}\label{newc}
    C_i\cup\{u_i\}
\end{equation}
and due to their independence at \ref{col: nullchainS}, we have a linearly independent set of size $$dim(T(V))+l.$$
If $l=dim (ker(L))$, we are done because of dimension theorem - the collection of the newly constructed nullchains at (\ref{newc})  is the desired basis .\\ \\
If otherwise, extend the linearly independent set $\{\beta_{11}, \beta_{21},...,\beta_{l1}\}$into a basis of $ker(L)$: $${\beta_{11}, ...,\beta_{l1}, w_{l+1},w_{l+2}...,w_{dimker(L)}}$$Then we have constructed new $dim ker(L)-l$ chains - all of size 1. \\ \\
Collecting everything, we have:
\[
\begin{aligned}
&\{w_{dimker(L)}\},\\
&\{w_{dimker(L)-1}\},\\
&\vdots\\
&\{w_{l+1}\}\\
&C_1\cup \{u_1\}\\
&C_2\cup \{u_2\}\\
&\vdots\\
&C_l \cup \{u_l\}.
\end{aligned}
\]
The union of everything above is a lin. ind. set due to \ref{col: nullchainS}, and it is of size $$dim\ (ker(L))-l+dim\ (T(V)) + l=$$ $$=dim\ (ker(L))+dim\ (T(V)),$$which means that it is a basis due to dimension theorem.


\end{proof}

Therefore since $T-\lambda_iI$ is nilpotent on $G_{\lambda_i}$, by the above theorem we may construct a nice-behaving basis $\beta_i$, composed of nullchains, for $G_{\lambda_i}$.
Let us consider the matrix representation of $\beta_i$ under $T$. \\ \\
We now proceed to show that they, as extensions of each $E_{\lambda_i}$, respectively, are now enough to span the whole space. Namely:$$\bigoplus_{i=1}^mG_{\lambda_i}=V$$
- then $\bigcup_{i=1}^m\beta_i$ may be our basis for the whole space. For this to first make sense, we need to make sure that that the $\Gi$ are mutually disjoint, and in some sort independent - meaning their bases are a lin. ind. set. \\ \\
\begin{theorem}\label{thrm: disj}
    $i\neq j\implies G_{\lambda_i}\cap G_{\lambda_j}=\{0\}  $
\end{theorem}
\begin{proof} The claim is equivalent to:  
\begin{align}
v\in G_{\lambda_i}\cap G_{\lambda_j}
\implies v=0 
\end{align}
which is equivalent to
\begin{align}
(T-\lambda_i I)^{k_1}(v)=(T-\lambda_j I)^{k_2}(v)=0\implies v=0.
\end{align}
(definition of $G_{\lambda_i},$ $G_{\lambda_j}$) where $k_1,k_2\in \mathbb{N^*}.$
Before we start, we first show the following weaker version.

\begin{claim}\label{cl:disj}
    $i\neq j \implies E_{\lambda_i}\cap G_{\lambda_j}=\{0\}$
\end{claim}

\textit{Proof.}
    Let $u\in E_{\lambda_i}\cap G_{\lambda_j}$. Then, \begin{equation}
    \label{eq:eigen}
    T(u)=\lambda_i u
\end{equation} and $\exists k\in \mathbb{N}^*$ s.t
\begin{equation}
\label{eq:chain}
    (T-\lambda_j\id)^k(u)=0.
\end{equation}
However,
$$(\ref{eq:eigen})\implies (T-\lambda_j\id)(u)=(\lambda_i - \lambda_j)(u)\implies(T-\lambda_j\id)^k(u)=(\lambda_i-\lambda_j)^k(u) $$and therefore $$(\ref{eq:chain})\implies (\lambda_i-\lambda_j)^k(u)=0\implies u=0$$because $i\neq j$.\hfill $\blacksquare$ \\ \\
Having this, consider $u=(T-\lambda_i\id)^{k_1-1}(v)$. Then,
\begin{equation}\label{5}
(T-\lambda_i\id)^{k_1}(v)=(T-\lambda_i\id)(u)=0\implies u\in E_{\lambda_i}.
\end{equation}
However note that $$v\in G_{\lambda_j}\implies (T-\lambda_i\id)(v)\in G_{\lambda_j}$$due to the invariance of $G_{\lambda_j}$ under $T-xI$ at \ref{col: invariance3}.
\begin{equation}\label{6}
    \implies u=(T-\lambda_i\id)^{k_1-1}(v)\in G_{\lambda_j}\implies u\in G_{\lambda_j} 
\end{equation}
Therefore (\ref{5}) and (\ref{6}) together with Claim \ref{cl:disj} imply $$u=0\implies (T-\lambda_j\id)^{k_1-1}(v)=0.$$
Similarly, letting $u_1=(T-\lambda_j\id)^{k_1-2}(v)$, the same approach implies $u_1=0$. Continuing this process inductively we arrive at $v=0.$



\end{proof}

This sets us up one step further for considering $$\bigoplus_{i=1}^m G_{\lambda_i}.$$We now need independence.
\begin{theorem}
    For a basis $\beta_i$ of $G_{\lambda_i}$, the set $$\bigcup_i\beta_i$$is linearly independent
\end{theorem}
\begin{proof}
    From Theorem \ref{thrm: disj}, all the $G_{\lambda_i}$ are mutually disjoint (except at $0$). Therefore, it is sufficient to show that for $u_i\in G_{\lambda_i}$,
    \begin{equation}\label{8}
    u_1+u_2+...+u_m=0
    \end{equation}
    implies $u_i=0\ \forall i\leq k.$\\
    For each $u_i,\ \exists a_i\in \mathbb{N}^*$ s.t 
    \begin{equation}
        (T-\lambda_i\id)^{a_i}(u_i)=0
    \end{equation}
     The invariance at Corollary \ref{col: invariance3} gives 
     \begin{equation}\label {10} 
     u_i\in G_{\lambda_i}\implies (T-x\id)(u_i)\in G_{\lambda_i}\ \forall x\in \C
     \end{equation}
     Now apply $(T-\lambda_1\id)^{a_1}$ to both sides in (\ref{8}) to vanish the first term and obtain
     \begin{equation}\label{11}
     0+(T-\lambda_1\id)^{a_1}(u_2)+...+(T-\lambda_1\id)^{a_m}(u_m)=0.
     \end{equation}
     Note that (\ref{10}) implies $(T-\lambda_1\id)^{a_1}(u_i)$ is still in $G_{\lambda_i}$ for $2\leq i\leq m$, so now we apply $(T-\lambda_2\id)^{a_2}$ to both sides in (\ref{11}) to vanish the second term, then $(T-\lambda_3\id)^{a_3}$ to vanish the third term, etc. At the end, we obtain
     \begin{equation}
         (T-\lambda_{m-1}\id)^{a_{m-1}}...(T-\lambda_2\id)^{a_2}(T-\lambda_1\id)^{a_1}(u_m)=0
     \end{equation}
     But then disjointness (Theorem \ref{thrm: disj}) implies $u_m=0$. Substituting back in $(\ref{8})$ and repeating the same process gives $$u_1=u_2=...=u_m=0$$
\end{proof}

Now that $G_{\lambda_i}$ are mutually disjoint and in a sense independent, the subspace
\begin{equation}\label{13}
    \bigoplus_{i=1}^{m}G_{\lambda_i}
\end{equation}
makes perfect sense. Before we jump to our final step - showing that (\ref{13}) gives $V$, let us see how the matrix representation of $T$ under the set $$\bigcup_{i=1}^m \beta_i$$would look like if it were a basis, where $\beta_i$ is a basis of $G_{\lambda_i}$ composed of nullchains under the map $T-\lambda_iI$ - as in Theorem \ref{theorem:multnull}. We have:

    \[
    [T]_{\cup \beta_i}=
    \begin{pmatrix}
    A_1 & 0   & \cdots & 0 \\
    0   & A_2 & \cdots & 0 \\
    \vdots & \vdots & \ddots & \vdots \\
    0   & 0   & \cdots & A_m
    \end{pmatrix}
    \]
    where each $A_i$ corresponds to the behaviour of $\beta_i$ and is of form
    \[
    A_i=
    \begin{pmatrix}
    \lambda_i & \star & 0 & \cdots & 0\\
    0 & \lambda_i & \star & \cdots & 0\\
    0 & 0 & \cdots & \ddots & \vdots\\
    \vdots & \vdots & \ddots & \ddots & \star\\
    
    0 & 0 & \cdots & 0 & \lambda_i
    \end{pmatrix}.
    \]
    where $$\star\in\{0,1\}$$
    This is the Jordan form.

    Note that this is a matrix representation for $T$ only if $\bigcup \beta_i$ is a basis for $V$. Therefore, we prove:
    \begin{theorem}
        $$\bigoplus_{i=1}^m \Gi = V$$
    \end{theorem}

    \begin{proof}
         Let $$W=\bigoplus_{i=1}^m G_{\lambda_i}$$and assume $W\neq V$.\\ \\
\begin{lemma}\label{lem:Winv}
    $W$ is invariant under $T-xI$ for any $x\in\mathbb{C}$
\end{lemma} 

\begin{proof}
    Invariance in each $G_{\lambda_i}$ due to \ref{col: invariance3} implies invariance in $W$.
\end{proof} 

The following result is most crucial in proving the theorem.
\begin{lemma}\label{lem:important}
    $v\notin W \implies (T-xI)(v)\notin W \ \forall x\in \mathbb{C}$
\end{lemma} 
\begin{proof}
    Assume for contradiction $\exists v\notin W$ s.t $(T-xI)
(v):=u\in W$.\\ \\
Case 1: $T-xI$ is invertible.\\
Then it is also invertible in $W$ due to the invariance at \ref{lem:Winv}. $$\implies \exists u_1 \in W \ s.t\ (T-xI)(u_1)=u.$$
But this means $(T-xI)(v)=(T-xI)(u_1)\implies v=u_1,$ a contradiction with $v \notin W$.\\ \\
Case 2: $ker (T-xI)\neq \emptyset$\\
This in particular means $x$ is an eigenvalue for $T$, and $$\bigcup_{k\in \mathbb{N}} ker(T-xI)^k=G_x\subseteq W$$due to definition of $W$.
Let $$T_x:=T-xI \text{ and } d=dim\ G_x$$and consider the linear map $T_x^d$.\\\\
By definition of $G_x,$ $$ker(T_x^d)=G_x$$
Because $W$ is invariant under $T_x$, we may apply
dimension theorem for the map $T_x^d$ restricted on $W$:
\begin{equation}
    \label{eq:dimW}
    dim(W)=dim\ T_x^d(W) +d
\end{equation}
Because $G_x$ is the generalized kernel of $T_x$, due to (\ref{initial}) at the initial examples we have 
\begin{equation}
    \label{eq:exclusion}
    v\notin G_x \implies T_x(v)\notin G_x
\end{equation}

This means that for each vector $w\in W$:
\begin{equation}
    T_x^d(w)=\begin{cases}
0, & w\in G_x,\\
\notin G_x & w\notin G_x.
\end{cases}
\end{equation}
and therefore $$T_x^d(W)\cap G_x=\{0\}$$
Together with (\ref{eq:dimW}), this implies
$$W=T_x^d(W) \oplus G_x$$
Now, recall our approach: we assumed by contradiction $$T_x(v)\in W$$for $v\notin W.$ By the direct-sum property, $T_x(v)\in W \implies \exists s\in T_x^d(W)$ and $g\in G_x$ s.t
$$T_x(v)=s+g$$
But, there clearly exists $u_1\in W$ s.t $T_x(u_1)=s$ ($s$ is in image of $T_x)$.
Thus, 
\begin{equation}
    \label{eq:dif}
    T_x(v)=T_x(u_1)+g\implies T_x(v-u_1)=g\in G_x
\end{equation}
But, $v\notin W$ and $u_1\in W$ implies $v-u_1\notin W$, and in particular not in $G_x$.
But together with (\ref{eq:dif}) this contradicts (\ref{eq:exclusion}).

Therefore, $$v\notin W\implies T_x(v)\notin W\implies (T-xI)(v)\notin W$$
\end{proof}


We are now ready to conclude the theorem. Lemma \ref{lem:important} implies $$v\notin  W\implies T^k(v)\notin W\ \forall k\in \mathbb{N}$$Consider $v,T(v),T^2(v),...,T^n(v)$ where $n=dim\ V$. These are $n+1$ vectors, thus linearly dependent. Therefore there exists $a_1,...,a_{n+1}$, $a_j\neq 0$ for some $j\leq n+1$ s.t $$a_0v+a_1T(v)+...+a_nT^n(v)=0$$ $$\implies(a_0+a_1T+a_2T^2+...+a_nT^n)(v)=0$$(linearity). Since we are working over complex field, the above can be factorized: $$(T-x_1I)^{k_1} (T-x_2I)^{k_2}...(T-x_mI)^{k_m}(v)=0\ (*)$$But $v\notin W$ and therefore $(T-xI)(v)\notin W\ \forall x\in \mathbb{C}$, so LHS of $(*)$ can never reach $0$, contradiction. 

Thus, we cannot have $V\neq W$ in the beginning.

\end{proof}

    
    






























 




\end{document}
