\section{Invariant subspaces}
\lettrine{C}{onsider}
a linear operator \( T \in \lmap(\vsV) \), where \(\vsV\) is a finite dimensional vector space.
For any subspace \(\vsS \subset \vsV\) the image of \(T\) over \(\vsS\) is, in general, some other arbitrary subspace.
It is natural then to want to consider subspaces which preserve their structure under \( T \). The following definition captures this idea.
\begin{definition}
    A subspace \( \vsS \) is called \textit{invariant} under the linear map \( T \) if

    \begin{equation*}
        \vv \in \vsS \implies T\vv\in \vsS
    \end{equation*}
\end{definition}


It is best to give some examples of such subspaces before investigating them further:

\subsection{Examples and properties}

\begin{example}
    The subspace called the eigenspace of \(T\) at eigenvalue \(\lambda\)
    \begin{equation*}
        E_\lambda = \{\vv: T\vv=\lambda \vv\}
    \end{equation*}

    is invariant - each element is scaled under \(T\), which is still in \(E_\lambda\).
\end{example}


\begin{example}\label{ex:invariance0}
    The image

    \begin{equation*}
        \im T=\{T\vv: \vv\in\vsV\}
    \end{equation*}

    is invariant by definition:
    \begin{equation*}
        \vv\in T(\vsV)\implies T\vv\in T(\vsV)
    \end{equation*}
\end{example}

\begin{example}\label{ex:invariance1}
    The generalized kernel

    \begin{equation*}
        K=\{\vv: \exists k\in \N \text{ s.t } T^k\vv=\0\}
    \end{equation*}

    is invariant under \( T \).
    This is indeed a subspace, and the invariance here follows from its definition.
    \begin{equation*}
        \vv\in K \implies \exists k,\; T^k\vv=\0 \implies T^{k-1}T\vv=\0 \implies T\vv\in K
    \end{equation*}

    This set has a stronger structure than being just invariant. It can be seen that
    \begin{equation}
        \vv\notin K\implies T\vv\notin K \label{eq:initial}
    \end{equation}
    which is not in general true for invariant subspaces.
\end{example}


\begin{figure}
    \centering
    \begin{tikzpicture}[scale=2]
        \draw[
            fill=blue!20,
            draw=blue!80!black,
            line width=1pt
        ] (0,0) ellipse [x radius=1cm, y radius=1.2cm];

        \node [right] (A) at (-0.45,0.5) {\( \vv \)};
        \node [right] (B) at (0.15,-0.5) {\( T\vv \)};
        \node at (0, 1.4) {\( \vsS \)};

        \draw[->, line width=1.25pt] (A) to[bend left=30] (B);

    \end{tikzpicture}
    \caption{A subspace \( \vsS \) invariant  under \(T\)}
\end{figure}

Because of their behavior, we want to search for building blocks of \( \vsV \) of invariant subspaces - similarly to how primes are building blocks of the integers.
By building blocks, we mean invariant subspaces

\begin{equation*}
    \vsS_1,\vsS_2,...,\vsS_k
\end{equation*}

such that for a basis \(\beta_i\) for \(\vsS_i\),
\begin{equation*}
    \bigcup_{i=1}^k \beta_i
\end{equation*}

is a basis for \( \vsV \).
Equivalently,
\begin{equation*}
    \bigoplus_{i=1}^k\vsS_k=\vsV
\end{equation*}

If we one succeeds in this, then there would be a matrix representation of \(T\) in the form

\[
    \begin{pmatrix}
        A_1    & 0      & \cdots & 0      \\
        0      & A_2    & \cdots & 0      \\
        \vdots & \vdots & \ddots & \vdots \\
        0      & 0      & \cdots & A_k
    \end{pmatrix}
\]

This structure is strictly due to the invariance of the subspaces - if \(\beta_i\) is a basis for \( \vsS_i \) consisting of \(\beta_{i1},\beta_{i2},...,\beta_{ik}\), then

\begin{equation*}
    T(\beta_{ij})\in \vsS_i\ \forall j\leq k,
\end{equation*}

and therefore may be expressed only in terms of \(\beta_{i1},\beta_{i2},...,\beta_{ik}\) - hence the above pattern.

\vspace{\baselineskip}

Our goal is to achieve this decomposition with choosing the best possible invariant subspaces - so that the above \(A_i\) blocks are of the simplest scheme.

It should already be obvious which invariant subspaces to start from. Before continuing, some properties:


\begin{property}
    Invariant subspaces (except \(\{\0\}\)) \(\vsS\) under \(T\) all contain an eigenvector of \(T\). This is for the reason that the linear map

    \begin{equation*}
        T^*:\vsS\rightarrow \vsS\ \text{,} \ T^*\vv=T\vv
    \end{equation*}

    is well defined due to the invariance. Then we just pick the eigenvector of \( T^* \) (always exists).

\end{property}

\begin{lemma}\label{lem:invariance2}
    \begin{equation*}
        \vsS\ \text{invariant under } T\iff \vsS\ \text{invariant under } T-x\id\ \forall x\in \C,
    \end{equation*}

    and consequently invariant under any polynomial \(P(T)\).
\end{lemma}

\section{The Jordan form}
\subsubsection{Statement}
For a linear operator \(T \in \lmap(\vsV)\) where \(\vsV\) is finite dimensional, there is a matrix representation of \(T\) of the form
\begin{equation*}
    \begin{pmatrix}
        J_1    & 0      & \cdots & 0      \\
        0      & J_2    & \cdots & 0      \\
        \vdots & \vdots & \ddots & \vdots \\
        0      & 0      & \cdots & J_k
    \end{pmatrix}
\end{equation*}

where \(J_i\) is a square matrix of the form

% Note:
% Question: are the k blocks meant to be jordan block or jordan matrix of each eigenvalue?

\begin{equation*}
    \begin{pmatrix}
        \lambda    & 1      & \cdots & 0      \\
        0      & \lambda    & \cdots & 0      \\
        \vdots & \vdots & \ddots & 1 \\
        0      & 0      & \cdots & \lambda
    \end{pmatrix}
\end{equation*}
\subsection{Method}

We start with considering the simplest invariant subspaces - the eigenspaces. Let the eigenvalues be \(\lambda_1, \lambda_2,...,\lambda_\sigma\) for a linear operator \(T\) over \(\vsV\), and the corresponding eigenspaces

\begin{equation*}
    E_{\lambda_{i}}=\{v: T\vv=\lambda_i \vv\}
\end{equation*}

It is important to know that

\begin{equation*}
    E_{\lambda_i}\cap E_{\lambda_j}=\{\0\}  \ \text{, for all }i<j\leq k,
\end{equation*}

and that for an arbitrary basis \(\beta_i\) for \(E_{\lambda_i}\), the set

\begin{equation*}
    \bigcup_{i=1}^{\sigma} \beta_i
\end{equation*}

is linearly independent.

\begin{figure}[H]
    \centering
    \begin{tikzpicture}[scale=2]
        \foreach \angle/\color/\labeltext in {0/blue/\(E_{\lambda_1}\), 120/teal/\(E_{\lambda_2}\), 240/purple/\(E_{\lambda_3}\)} {
                \begin{scope}[rotate=\angle]
                    \draw[fill=\color!20, draw=\color!80!black, line width=1pt]
                    (0,1.5) .. controls (-0.7,1.4) and (-0.8,0.6) .. (0,0)
                    .. controls (0.8,0.6) and (0.7,1.4) .. (0,1.5) -- cycle;
                    \node[ font=\bfseries\sffamily] at (0,0.8) {\labeltext};
                \end{scope}
                \node[
                    below right,          % Position relative to (0,0)
                    font=\small\sffamily  % Clean font style
                ] at (0,0) {\(\0\)};
            }
    \end{tikzpicture}
    \caption{Three eigenspaces of some map \(T\)}
\end{figure}


Is \(\bigoplus_{i=1}^{\sigma} E_{\lambda_i} = \vsV\) true? - if yes, \(\bigcup \beta_i\) may be our basis.
Sadly, this is often not the case. An example is the matrix

\begin{equation*}
    A = \begin{pmatrix}
        1 & 1 & 0 \\
        0 & 1 & 1 \\
        0 & 0 & 1
    \end{pmatrix}
\end{equation*}

with its corresponding linear map. If \(\bigoplus E_{\lambda_i}\) is not enough to cover \(\vsV\), we want to somehow expand each \(E_{\lambda_i}\) into a bigger subspace, with the importance to keep their invariance and disjointedness.


\subsection{Generalising the eigenspaces}

For each \(E_{\lambda_i}\), consider

\begin{equation*}
    \boxed{
        \vsG_{\lambda_i}=\bigcup_{i=1}^{\infty} \ker(T-\lambda_i \id)^k
    }
\end{equation*}


Intuitively this can be thought of as extending the subspace to include vectors that are 'close' to becoming eigenvectors.
In the sense that they are a finite number of iterations of \(T- \lambda_i\id\) away from \(\0\).

Denote

\begin{equation*}
    X^k_i:=\ker(T-\lambda_i \id)^k
\end{equation*}

and notice that \( E_{\lambda_i}=X^1_i\).
It can be seen that \(X^k_i\subseteq X^{k+1}_{i}\).
This means that for each iteration of \(k\), the subspace \(X^k_i\) grows, seen in Figure \ref{fig:geneigen}.
Each \(X^k_i\) has two nice properties: it is nilpotent under \(T-\lambda_i\id\), and invariant under \(T-x\id\ \forall x\in \C \) which actually follows from the former.

\begin{lemma}
    For each \(k\in \N\), \(X^k_i\) is invariant under \(T-x\id\ \forall x\in \C\)
\end{lemma}

\begin{proof}
    Follows from \ref{ex:invariance1} together with \ref{lem:invariance2}
\end{proof}

Notice that because \(X^k_i\subseteq X^{k+1}_{i}\subseteq \vsV \ \forall k\), after some iteration \(N\in\N\), we must have

\begin{equation*}
    X^k_i=X^{k+1}_{i}\  \forall k\geq N
\end{equation*}

since we are bounded by the dimension of \(\vsV\).

The final extendable subset is \(\vsG_{\lambda_i}=X^N_i\).

\begin{corollary}\label{col:invariance3}
    \(\vsG_{\lambda_i}\) is invariant under \(T-x\id\ \forall x\in \C.\)
\end{corollary}
\begin{figure}[H] \label{fig:geneigen}
\centering
    \begin{tikzpicture}
        % (horizontal radius, vertical radius)
        \foreach \a/\clr/\b in {
            2.0/blue/4,
            1.5/teal/3,
            1.0/purple/2
        }{
            \draw[thick, fill=\clr!20, draw=\clr!80!black, line width=1pt] (0,\b) ellipse [x radius=1.5 * \a, y radius=\b];
        }
        \node[above] at (0, 2) {\(E_{\lambda_i}\)};
        \node[above] at (0, 5) {\(\ker (T - \lambda _i\id)^{2}\)};
        \node[above] at (0, 7) {\(\ker (T - \lambda _i\id)^{3}\)};

        \node[below] at (0,0) {\( \0 \)};
        % optional coordinate marker
        \fill (0,0) circle (1.5pt);
    \end{tikzpicture}
    \caption{The generalised eigenspace \( \vsG_{\lambda_i} \) of the eigenvalue \(\lambda _i\). In this case \( \vsG_{\lambda_i} \) stops growing at \(\ker (T - \lambda _i\id)^{3} \).}
\end{figure}
\subsection{Introducing the null-chains}

There is an appropiate way to pick a basis for \(\vsG_{\lambda_i}\). Recall that each \(\vv\in \vsG_{\lambda_i}\) eventually gets mapped to \(\0\) under \(T-\lambda_i\id\) (in other words, \(T-\lambda_i I\) is nilpotent on \(\vsG_{\lambda_i}\)), so it is natural to define the following set:

\begin{definition}
    A \textit{null-chain} under  linear map \(L\) is a set of (one or more) \textbf{non-zero} vectors \(\{\vv_1,\vv_2,..\vv_n\}\)

    such that

    \begin{equation*}
        L(\vv_{i+1})=\vv_{i}\text{ for }i\leq n-1
    \end{equation*}

    and

    \begin{equation*}
        L(\vv_1)=0
    \end{equation*}
\end{definition}

\begin{figure}[H]
    \centering
     \begin{tikzpicture}[font=\small]
        % (horizontal radius, vertical radius)
        \foreach \a/\clr/\b in {
            2.0/blue/4,
            1.5/teal/3,
            1.0/purple/2
        }{
            \draw[thick, fill=\clr!20, draw=\clr!80!black, line width=1pt] (0,\b) ellipse [x radius=1.5 * \a, y radius=\b];
        }
        \node[above left] at (0, 2) {\(E_{\lambda_i}\)};
        \node[above left] at (0.5, 4.5) {\(\ker (T - \lambda _i\id)^{2}\)};
        \node[above left] at (0.5, 6.5) {\(\ker (T - \lambda _i\id)^{3}\)};

        \node[below] at (0,0) {\( \0 \)};

        % null chain
        \node [right] (A) at (1.3,6) {\(\vv_3\)};

        \node [right] (B) at (1.25,3.5) {\(\vv_2\)};

        \node [right] (C) at (0.25,1.5) {\(\vv_1\)};

        % lines
        \draw[->, line width=1.20pt] (A) to[bend left=30] node[right, font=\small\bfseries] {\(T- \lambda_i\id\)} (B);


        \draw[->, line width=1.25pt] (B) to[bend left=30] node[right, font=\small\bfseries] {\(T- \lambda_i\id\)} (C);

        \draw[->, line width=1.25pt] (C) to[bend left=30] node[right, font=\small\bfseries] {\(T- \lambda_i\id\)} (0,0);


        \fill (0,0) circle (1.5pt);
    \end{tikzpicture}
    \caption{A null-chain \(\{v_1,v_2,v_3\}\) under \(T-\lambda_iI\) in a generalised eigenspace}
\end{figure}


As one may guess:
\begin{lemma}\label{lem:nullchain-indp}
    A null-chain under a linear map \( L \) forms a linearly independent set.
\end{lemma}

\begin{proof}
    Consider a null-chain

    \begin{equation*}
        \{\vv_1,\vv_2,...,\vv_n\}
    \end{equation*}

    and let
    \begin{equation}\label{eq:null}
        c_1\vv_1+c_2\vv_2+...+c_n\vv_n=\0.
    \end{equation}


    Applying \(L^{n-1}\) on both sides and considering null-chain properties gives

    \begin{equation*}
        c_1L^{n-1}(\vv_1)+...+c_nL^{n-1}(\vv_n)=\0\implies c_n\vv_1=\0\implies c_n=0.
    \end{equation*}

    Substituting back in \eqref{eq:null} and applying \(L^{n-2}\) on both sides gives

    \begin{equation*}
        c_{n-1}\vv_1=\0\implies c_{n-1}=0.
    \end{equation*}

    Continuing this inductive process we obtain

    \begin{equation*}
        c_1=c_2=...=c_n=0
    \end{equation*}
\end{proof}

\begin{corollary}\label{col:nullchainS}
    A collection of null-chains forms a linearly independent set.
\end{corollary}

% Note:
% I don't see why this is the case in general.
% Maybe you mean something else?

The argument for this is similar to Lemma \ref{lem:nullchain-indp}

We can pick null-chain in \(\vsG_{\lambda_i}\) under \(T-\lambda_i\id\) and check whether it is a basis for \(\vsG_{\lambda_i}\).
In general this is not the case.
For example consider the matrix

\begin{equation*}
    A=\begin{pmatrix}
        2 & 1 & 0 \\
        0 & 2 & 0 \\
        0 & 0 & 2
    \end{pmatrix}
\end{equation*}

Note that \(2\in\spec A\), with \(\dim\vsG_2=3\).
However, the longest null-chain for \(A-2I\) is of length \(2\), so one null-chain is not enough.

\subsection{Collecting the null-chains}
The idea is to pick multiple such chains. Then it can be shown:
\begin{theorem}\label{theorem:multnull}
    A non-zero finite-dimensional vector space \(\vsV\) under a nil-potent linear map \(L\) always has a basis composed of disjoint null-chains.
\end{theorem}
\begin{proof}
    % Note:
    % Maybe we could put it in an appendix instead?
    \textit{The proof of this is surprisingly lengthy and the reader may skip it - its ideas are important but are not all crucial for following work.}

    We show this via strong induction on the dimension of \(\vsV\).
    Consider a vector space \(\vsV\) under under a nilpotent map \(L\) with \( \dim\vsV=1 \).

    Any \(\vv\neq\0\in\vsV\) is a basis of \(\vsV\), and since \(L\vv=\0\), the null-chain

    \begin{equation*}
        \{\vv\}
    \end{equation*}

    is a basis.

    Now that we have our base case, let \( \dim\vsV=k \).

    We hypothesizing that:

    \textit{Every vector space with dimension \(\leq k-1\) which is nilpotent under \(L\) has a basis of disjoint null-chains.}

    The map \(L\) is obviously non-invertible on \(\vsV\), therefore
    \begin{equation}\label{eq:dim-image-bound}
        \dim L(\vsV)< \dim\vsV
    \end{equation}
    where \(L(\vsV)\) is the image \(L\) over \(\vsV\).

    Dimension theorem for \(L\) on \(V\) states
    \begin{equation}
        \dim\vsV=\dim L(\vsV) + \dim\ker L
    \end{equation}
    Note that \(L(\vsV)\) is a subspace of \(\vsV\), therefore it is also nilpotent under \(L\).
    Considering \eqref{eq:dim-image-bound}, by the induction hypothesis there is a basis of \(L(\vsV)\) of the form

    % TODO: read and understand the proof and evaluate its correctness
    % Also fix any styling error

    \begin{align*}
        C_1 & = \{\beta_{11}, \beta_{12}, \ldots, \beta_{1k_1}\}, \\
        C_2 & = \{\beta_{21}, \beta_{22}, \ldots, \beta_{2k_2}\}, \\
            & \vdots                                              \\
        C_l & = \{\beta_{l1}, \beta_{l2}, \ldots, \beta_{lk_l}\}. \\
    \end{align*}

    where \(C_i\)'s are \(l\) many disjoint nullchains such that

    \[
        \begin{aligned}
            L(\beta_{i1})     & = 0          \\
            L(\beta_{i(k+1)}) & = \beta_{ik}
        \end{aligned}
    \]

    We have that

    \[
        |\bigcup_{i=1}^l C_i|= \dim L(\vsV).
    \]

    Note that the first vector in each chain is in \( \ker(L)\) and therefore
    \begin{equation}
        l\leq \dim \ \ker(L)
    \end{equation}
    because of the linear independence of the \(\beta_{i1}\)'s.\\
    Consider the last vector \(\beta_{ik_i}\) in each chain - it is in \(L(V)\), therefore
    \begin{equation}
        \forall i\leq l, \exists u_i\ s.t \ L(u_i)=\beta_{ik_i}
    \end{equation}
    Thus we have upgraded our initial chains by adding one more vector
    \begin{equation}
        C_i\cup\{u_i\} \label{eq:newc}
    \end{equation}
    and due to their independence at \ref{col:nullchainS}, we have a linearly independent set of size

    \[
        \dim(L(V))+l.
    \]

    If \(l=\dim (\ker(L))\), we are done because of dimension theorem - the collection of the newly constructed nullchains at \eqref{eq:newc}  is the desired basis .\\ \\
    Otherwise, extend the linearly independent set \(\{\beta_{11}, \beta_{21},...,\beta_{l1}\}\)into a basis of \(\ker(L)\): \[
        {\beta_{11}, ...,\beta_{l1}, w_{l+1},w_{l+2}...,w_{\dim \ker(L)}}
    \]

    Then we have constructed new \(\dim \ker(L)-l\) chains - all of size 1. \\ \\
    Collecting everything, we have:
    \[
        \begin{aligned}
             & \{w_{\dim \ker(L)}\},   \\
             & \{w_{\dim \ker(L)-1}\}, \\
             & \vdots                  \\
             & \{w_{l+1}\}             \\
             & C_1\cup \{u_1\}         \\
             & C_2\cup \{u_2\}         \\
             & \vdots                  \\
             & C_l \cup \{u_l\}.
        \end{aligned}
    \]

    The union of everything above is a linearly independent set due to \ref{col:nullchainS}, and it is of size

    \[
        \dim\ (\ker(L))-l+\dim\ (T(V)) + l=
    \] \[
        =\dim\ (\ker(L))+\dim\ (T(V)) = \dim V,
    \]

    which means that it is a basis due to dimension theorem.


\end{proof}

Therefore, since \(T-\lambda_i\id\) is nilpotent on \(\vsG_{\lambda_i}\), by the above theorem we may construct an appropriate basis \(\beta_i\) - composed of nullchains - for \(\vsG_{\lambda_i}\).

Let us consider the matrix representation of \(\beta_i\) under \(T\).

A single null-chain in its decomposition has the following structure:

\begin{align*}
    (T-\lambda_i\id)\vv_1   & = \0          \\
    (T-\lambda_i\id)\vv_2   & = \vv_1       \\
    \vdots                                  \\
    (T-\lambda_i\id)\vv_n   & = \vv_{n-1}   \\
\end{align*}


which in terms of \(T\) gives

\begin{align*}
    T\vv_1 & = \lambda_i \vv_1              \\
    T\vv_2 & = \lambda_i \vv_2 + \vv_1      \\
    \vdots                                  \\
    T\vv_n & = \lambda_i \vv_n + \vv_{n-1}  \\
\end{align*}

Putting this in a matrix pattern gives
\begin{equation}
    J_1=
    \begin{pmatrix}
        \lambda_i & 1         & 0      & \cdots & 0         \\
        0         & \lambda_i & 1      & \cdots & 0         \\
        0         & 0         & \cdots & \ddots & \vdots    \\
        \vdots    & \vdots    & \ddots & \ddots & 1         \\

        0         & 0         & \cdots & 0      & \lambda_i \\
    \end{pmatrix}
    \label{eq:jordanblock}
\end{equation}


This structure is called a Jordan block. Since the basis \(\beta_i\) is composed of multiple null-chains, its matrix pattern gives
\begin{equation}
    J=
    \begin{pmatrix}
        J_1    & 0      & \cdots & 0      \\
        0      & J_2    & \cdots & 0      \\
        \vdots & \vdots & \ddots & \vdots \\
        0      & 0      & \cdots & J_k
    \end{pmatrix}
    \label{eq:jordan-form}
\end{equation}
where each \(J_i\) is of form \eqref{eq:jordanblock}



\subsection{Spanning the vector space}
We proceed to show that all \( \vsG_i \)  - as extensions of each \(E_{\lambda_i}\) - are enough to span the whole space.
Namely:
\begin{equation*}
    \bigoplus_{i=1}^\sigma G_{\lambda_i}=V
\end{equation*}

If this is true, then \(\bigcup_{i=1}^m\beta_i\) may be our basis for the whole space, where $\beta_i$ is a basis for $G_{\lambda_i}$.
For this to first make sense, we need to make sure that that the \( \vsG_i \) are mutually disjoint, and in some sort independent - meaning the union of their bases are linearly independent.

\begin{theorem}\label{thm:disj}
    For any \(i\neq j\), we have
    \begin{equation*}
        \vsG_{\lambda_i}\cap \vsG_{\lambda_j}=\{\0\}
    \end{equation*}
    where \(\{\lambda_1,...,\lambda_\sigma\}\) is the spectrum of T and \(G_{\lambda}\) is the generalized eigenspace for \(\lambda\)
\end{theorem}

% TODO: Continue reading

\begin{proof} The claim is equivalent to:
    \begin{equation}
        \vv\in G_{\lambda_i}\cap G_{\lambda_j}
        \implies \vv=0
    \end{equation}

    We first show the following weaker version.

    \begin{claim}\label{cl:disj}
        \(i\neq j \implies E_{\lambda_i}\cap G_{\lambda_j}=\{0\}\)
    \end{claim}

    \textit{Proof.}
    Let \(u\in E_{\lambda_i}\cap G_{\lambda_j}\). Then, \begin{equation}
        \label{eq:eigen}
        T(u)=\lambda_i u
    \end{equation} and \(\exists k\in \N\) s.t
    \begin{equation}
        \label{eq:chain}
        (T-\lambda_j\id)^k(u)=0.
    \end{equation}

    However,
    \[
        \eqref{eq:eigen}\implies (T-\lambda_j\id)(u)=(\lambda_i - \lambda_j)(u)\implies(T-\lambda_j\id)^k(u)=(\lambda_i-\lambda_j)^k(u)
    \]

    and therefore

    \[
        \eqref{eq:chain}\implies (\lambda_i-\lambda_j)^k(u)=0\implies u=0
    \]

    because \(i\neq j\).\hfill \(\blacksquare\) \\ \\

    Let \(v\in \vsG_i \cap G_{\lambda_j}\). This means \(\exists k_1,k_2\in \N\) such that
    \begin{equation}
        (T-\lambda_iI)^{k_1}(v)=(T-\lambda_jI)^{k_2}(v)=0
    \end{equation}
    (definiton of \(\vsG_i,G_{\lambda_j}\)). Having this, consider \(u=(T-\lambda_i\id)^{k_1-1}(v)\). Then,
    \begin{equation}\label{eq:u-in-eigenspace}
        (T-\lambda_i\id)^{k_1}(v)=(T-\lambda_i\id)(u)=0\implies u\in E_{\lambda_i}.
    \end{equation}
    However note that

    \[
        v\in G_{\lambda_j}\implies (T-\lambda_i\id)(v)\in G_{\lambda_j}
    \]

    due to the invariance of \(G_{\lambda_j}\) under \(T-xI\) at \ref{col:invariance3}.
    \begin{equation}\label{eq:u-in-generalized-eigenspace}
        \implies u=(T-\lambda_i\id)^{k_1-1}(v)\in G_{\lambda_j}\implies u\in G_{\lambda_j}
    \end{equation}
    Therefore \eqref{eq:u-in-eigenspace} and \eqref{eq:u-in-generalized-eigenspace} together with Claim \ref{cl:disj} imply

    \[
        u=0\implies (T-\lambda_j\id)^{k_1-1}(v)=0.
    \]

    Similarly, letting \(u_1=(T-\lambda_j\id)^{k_1-2}(v)\), the same approach implies \(u_1=0\). Continuing this process inductively we arrive at \(v=0.\)


\end{proof}

This sets us up one step further for considering

\begin{equation*}
    \bigoplus_{i=1}^\sigma \vsG_{\lambda_i}.
\end{equation*}

Another property we need is independence.
\begin{theorem}
    If \(\beta_i\) is a basis of the generalised eigenspace \(\vsG_{\lambda_i}\), then the set

    \begin{equation*}
        \bigcup^{\sigma}_{i=1}\beta_i
    \end{equation*}

    is linearly independent.
\end{theorem}
\begin{proof}
    From Theorem \ref{thm:disj}, all the \(G_{\lambda_i}\) are mutually disjoint. Therefore, it is sufficient to show that for \(u_i\in G_{\lambda_i}\),
    \begin{equation}\label{eq:sum-ui-zero}
        u_1+u_2+...+u_\sigma=0
    \end{equation}
    implies \(u_i=0\ \forall i\leq k.\)\\ \\
    For each \(u_i,\ \exists a_i\in \N\) s.t
    \begin{equation}
        (T-\lambda_i\id)^{a_i}(u_i)=0
    \end{equation}
    The invariance at Corollary \ref{col:invariance3} gives
    \begin{equation}\label{eq:generalized-eigenspace-invariance}
        u_i\in G_{\lambda_i}\implies (T-x\id)(u_i)\in G_{\lambda_i}\ \forall x\in \C
    \end{equation}
    Now apply \((T-\lambda_1\id)^{a_1}\) to both sides in \eqref{eq:sum-ui-zero} to vanish the first term and obtain
    \begin{equation}\label{eq:first-term-vanishes}
        0+(T-\lambda_1\id)^{a_1}(u_2)+...+(T-\lambda_1\id)^{a_\sigma}(u_\sigma)=0.
    \end{equation}
    Note that \eqref{eq:generalized-eigenspace-invariance} implies \((T-\lambda_1\id)^{a_1}(u_i)\) is still in \(G_{\lambda_i}\) for \(2\leq i\leq \sigma\), so now we apply \((T-\lambda_2\id)^{a_2}\) to both sides in \eqref{eq:first-term-vanishes} to vanish the second term, then \((T-\lambda_3\id)^{a_3}\) to vanish the third term, etc. At the end, we obtain
    \begin{equation}
        (T-\lambda_{\sigma -1}\id)^{a_{\sigma-1}}...(T-\lambda_2\id)^{a_2}(T-\lambda_1\id)^{a_1}(u_\sigma)=0
    \end{equation}
    But then disjointness (Theorem \ref{thm:disj}) implies \(u_\sigma=0\). Substituting back in \(\eqref{eq:sum-ui-zero}\) and repeating the same process gives

    \[
        u_1=u_2=...=u_\sigma=0
    \]
\end{proof}

Now that \(G_{\lambda_i}\) are mutually disjoint and in a sense independent, the subspace
\begin{equation}\label{eq:generalized-eigenspace-direct-sum}
    \bigoplus_{i=1}^{\sigma}G_{\lambda_i}
\end{equation}
makes perfect sense. Before we jump to our final step - showing that \eqref{eq:generalized-eigenspace-direct-sum} gives \(V\), let us see how the matrix representation of \(T\) on the set

\[
    \bigcup_{i=1}^\sigma \beta_i
\]

looks like, where \(\beta_i\) is the usual basis of \(G_{\lambda_i}\). We have:

\[
    [T]_{\cup \beta_i}=
    \begin{pmatrix}
        A_1    & 0      & \cdots & 0      \\
        0      & A_2    & \cdots & 0      \\
        \vdots & \vdots & \ddots & \vdots \\
        0      & 0      & \cdots & A_\sigma
    \end{pmatrix}
\]

where each \(A_i\) corresponds to \(\beta_i\) and is of form \eqref{eq:jordan-form}.\\ \\
This is the Jordan form.

Note that this is a matrix representation for \(T\) only if \(\bigcup \beta_i\) is a basis for \(V\). Therefore, we prove:
\begin{theorem}
    \[
        \bigoplus_{i=1}^\sigma \vsG_i = V
    \]
\end{theorem}

\begin{proof}
    Denote

    \[
        W:=\bigoplus_{i=1}^\sigma G_{\lambda_i}
    \]

    and assume \(W\neq V\).\\ \\
    \begin{lemma}\label{lem:Winv}
        \(W\) is invariant under \(T-xI\) for any \(x\in\C\)
    \end{lemma}

    \begin{proof}
        Invariance in each \(G_{\lambda_i}\) due to \ref{col:invariance3} implies invariance in \(W\).
    \end{proof}

    The following result is most crucial in proving the theorem.
    \begin{lemma}\label{lem:important}
        \(v\notin W \implies (T-xI)(v)\notin W \ \forall x\in \C\)
    \end{lemma}
    \begin{proof}
        Assume for contradiction \(\exists v\notin W\) s.t \((T-xI)
        (v):=u\in W\).\\ \\
        Case 1: \(T-xI\) is invertible.\\
        Then it is also invertible in \(W\) due to the invariance at \ref{lem:Winv}. \[
            \implies \exists u_1 \in W \ s.t\ (T-xI)(u_1)=u.
        \]

        But this means \((T-xI)(v)=(T-xI)(u_1)\implies v=u_1,\) a contradiction with \(v \notin W\).\\ \\
        Case 2: \(\ker (T-xI)\neq \emptyset\)\\
        This in particular means \(x\) is an eigenvalue for \(T\), and

        \[
            \bigcup_{i=1}^{\infty} \ker(T-xI)^i=G_x
        \]

         \[
         G_x\in W
         \]

        due to definition of \(W\).
        Let

        \[
            T_x:=T-xI \text{ and } d=\dim\ G_x
        \]

        and consider the linear map \(T_x^d\).\\\\
        By definition of \(G_x,\) \[
            \ker(T_x^d)=G_x
        \]

        Because \(W\) is invariant under \(T_x\), we may apply
        dimension theorem for the map \(T_x^d\) restricted on \(W\):
        \begin{equation}
            \label{eq:dimW}
            \dim(W)= \dim\ T_x^d(W) +\dim G_x
        \end{equation}
        Because \(G_x\) is the generalized kernel of \(T_x\), due to \eqref{eq:initial} at the initial examples we have
        \begin{equation}
            \label{eq:exclusion}
            v\notin G_x \implies T_x(v)\notin G_x
        \end{equation}

        This means that for each vector \(w\):
        \[
        \begin{aligned}
             & w\in G_x\implies T^d_x(w)=0 \\
          & w\notin G_x\implies T^d_x(w)\notin G_x
        \end{aligned}
    \]
        and therefore

        \[
            T_x^d(W)\cap G_x=\{0\}
        \]

        Together with \eqref{eq:dimW}, this implies

        \[
            W=T_x^d(W) \oplus G_x
        \]

        However we assume

        \[
            T_x(v)\in W
        \]

        for \(v\notin W.\) By the direct-sum property, \(T_x(v)\in W \implies \exists s\in T_x^d(W)\) and \(g\in G_x\) s.t

        \[
            T_x(v)=s+g
        \]

        But, there clearly exists \(u_1\in W\) s.t \(T_x(u_1)=s\) (\(s\) is in image of \(T_x)\).
        Thus,
        \begin{equation}
            \label{eq:dif}
            T_x(v)=T_x(u_1)+g\implies T_x(v-u_1)=g\in G_x
        \end{equation}
        But, \(v\notin W\) and \(u_1\in W\) implies \(v-u_1\notin W\), and in particular not in \(G_x\).
        But together with \eqref{eq:dif} this contradicts \eqref{eq:exclusion}.

        Therefore, \[
            v\notin W\implies T_x(v)\notin W\implies (T-xI)(v)\notin W
        \]
    \end{proof}


    We are now ready to conclude the theorem. Lemma \ref{lem:important} implies

    \[
        v\notin  W\implies T^k(v)\notin W\ \forall k\in \N
    \]

    Consider \(v,T(v),T^2(v),...,T^n(v)\) where \(n= \dim\ V\). These are \(n+1\) vectors, thus linearly dependent. Therefore there exists \(a_0,...,a_{n}\), \(a_j\neq 0\) for some \(j\leq n\) s.t

    \[
        a_0v+a_1T(v)+...+a_nT^n(v)=0
    \] \[
        \implies(a_0+a_1T+a_2T^2+...+a_nT^n)(v)=0
    \](linearity). Since we are working over the complex field, the above can be factorized:
    \begin{equation}
        (T-x_1I)^{k_1} (T-x_2I)^{k_2}...(T-x_mI)^{k_m}(v)=0 \quad m \leq n \tag{\(\star\)} \label{eq:star}
    \end{equation}

    But \(v\notin W\) and therefore \((T-xI)(v)\notin W\ \forall x\in \C\), so the left hand side of \eqref{eq:star} can never reach \(0\) as \(0 \in W\). Contradiction!

    Thus, we cannot have \(V\neq W\) in the beginning.

\end{proof}
